A Survey of Fuzzing and New Technique for Dynamic Analysis

### 2014-02-21 docs/paper/fsuthesis/thesis-template/paper.tex
finished javascript fuzzer paper

The GUI explorer handles the event space by exploring all possible sequences of user-defined events at random. In order to discover event handlers, the GUI explorer relies on information from Kudzu, which instruments WebKit functions. When an HTML element which can generate an event is found, or when one of these elements in removed, Kudzu's hooks notice this and inform the GUI explorer accordingly.

[AD]
new things contributed
challenges - js strings, GUI elements
arch. use WebKit browser, 
js example of challenge
shortcomings - don't support all string ops, nor all JavaScript regex functionality, tradeoff
results - lots of found vulns involve strings,

@@

@@

>>>>

The GUI explorer handles the event space by exploring all possible sequences of user-defined events at random. In order to discover event handlers, the GUI explorer relies on information from Kudzu, which instruments WebKit functions. When an HTML element which can generate an event is found, or when one of these elements in removed, Kudzu's hooks notice this and inform the GUI explorer accordingly. Symbolic execution is broken down into a custom constraint extractor, which acts upon an execution trace from a concrete execution of the program, looking for control-flow statements and whether they were taken given the appropriate values compared, and a custom constraint solver, purposefully designed to handle JavaScript objects, which receives symbolic constraints from the extractor. After the solver has reasoned about the constraints on some piece of input, a new input test case is generated and fed back into the system. Since symbolic execution is costly, Kudzu identifies when user input appears to flow to one of finitely many vulnerability sinks, such as eval or document.write. Only this user input is considered symbolically. As Kudzu runs, it takes new test cases and executes the program with a mix of symbolic and concrete variables, and checks to see whether input that flows to vulnerable sinks can result in an exploit, for instance by inserting JavaScript alerts and checking to see whether they execute [AD].

Like TODO Owen's thing, Kudzu tries to circumvent the issue of solving complicated constraints by first converting JavaScript into an intermediate language called JASIL. Strings, in particular, are parsed and partitioned into several sub types which are more uniform. For instance, one type handles strings which are semantically regular expressions, another handles strings which are the concatenation of two other strings. Although not as featureful as JavaScript strings, this IL captures a large enough number of String features to allow Kudzu to find previous unknown exploits in programs. Shortcomings include an incomplete support of String operations and JavaScript regular expressions, notably backreferences, which match a previously matched string in the regex. Although representation of strings is incomplete, Kudzu reasons well enough to find two new vulnerabilities, as well as 9 previous vulnerabilities [AD].

@@

TODO talk about how this is called many different things, and is a rather amorphous term.

@@

\section{TODO Conversion to an Intermediate Representation}

Used in javascript fuzzer [AD]
Used in Owen's slides.
